Vertical shear instability in astrophysical disks: vertically global linear calculations with thermal relaxation and applications to the Solar Nebula

### 2015-03-07 numerical.tex
commented out kx<1 comment, there is convec overstability

 Growth rates are expected to diminish for both $\khat\to 0$
  and $\khat\to \infty$. This is because for $\khat\ll 1$ the radial
  wavelenth is large, but such disturbances are 
  stabilized by by epicyclic motions ($|\omega|\sim
  \kappa$). Disturbances with $\khat\gg 1$ are radially localized, but  
  there is no energy change when fluid elements are perturbed at fixed
  cylindrical radius whilst conserving its angular momentum (since we
  consider axisymmetric perturbations).

@@

For $\khat\lesssim 10$, e.g. $\khat=1$ in 
Fig. \ref{lowfreq_eigenfunc}, the perturbation magnitude near the
boundaries begin to dominate. For even smaller $\khat\lesssim 1$ (not
shown) we find the perturbation is almost entirely concentrated at the
boundaries. However, our radially-local approximation is not valid for 
such small wavenumber perturbations.

>>>>

 With rapid thermal relaxation, growth rates are expected to diminish for both $\khat\to 0$
 and $\khat\to \infty$. This is because for $\khat\ll 1$ the radial
  wavelenth is large, but such disturbances are 
  stabilized by by epicyclic motions ($|\omega|\sim
  \kappa$). Disturbances with $\khat\gg 1$ are radially localized, but  
  there is no energy change when fluid elements are perturbed at fixed
  cylindrical radius whilst conserving its angular momentum (since we
  consider axisymmetric perturbations).

@@

%For $\khat\lesssim 10$, e.g. $\khat=1$ in 
%Fig. \ref{lowfreq_eigenfunc}, the perturbation magnitude near the
%boundaries begin to dominate. For even smaller $\khat\lesssim 1$ (not
%shown) we find the perturbation is almost entirely concentrated at the
%boundaries. However, our radially-local approximation is not valid for 
%such small wavenumber perturbations.
